Association between wildfire smoke and asthma claims by place of service

### 2018-06-19 r_scripts/analysis/asthma_place_of_service_analysis.Rmd
updated lag associaiton.

>>>>

## Lagged Associations

```{r lag_association}
# itterate over each geosmk
pm_vec <- c('geo_smk10', paste0('geo_smk10_lag', seq(1,5,1)))
temp_vec <- c('wrf_temp', paste0('wrf_temp_lag', seq(1,5,1)))

# map lag
lag_result <- asthma_pos_list %>% 
  map_dfr(., function(df){
    service_place <- as.character(df$service_place[1])
    # complete case up to lag day 5
    df <- df %>% filter(!is.na(geo_smk10_lag5))
    # lag map
    result <- map2_dfr(pm_vec, temp_vec, function(.x, .y){
      # model
      mod <- clogit(as.formula(paste0('outcome ~', 
             paste(.x, .y, 'strata(identifier)', sep = '+'))),
             data = df)
      # n events
      n_events <- mod$nevent
      # lag var
      lag_var <- pm_vec
      # odds ratio and 95% CI
        estimates <- broom::tidy(mod) %>% 
          #filter(term == lag_var) %>% 
          dplyr::select(term, estimate, conf.low, conf.high) %>% 
          mutate_at(2:4, funs(round(exp(.),3))) %>% 
          cbind(service_place, n_events, .) %>% 
          mutate(service_place = as.character(service_place))
    }) %>% filter(grepl('geo_smk10', term))
  }) %>% 
  mutate(strata = "Total",
         Lag = case_when(term == 'geo_smk10' ~ 'Lag 0',
                         term == 'geo_smk10_lag1' ~ 'Lag 1',
                         term == 'geo_smk10_lag2' ~ 'Lag 2',
                         term == 'geo_smk10_lag3' ~ 'Lag 3',
                         term == 'geo_smk10_lag4' ~ 'Lag 4',
                         term == 'geo_smk10_lag5' ~ 'Lag 5'))

# table
lag_result
```

Plot for lag.

```{r lag_plot}
glimpse(lag_result)

lag_result <- lag_result %>% 
  mutate(service_place = ifelse(service_place == 'Emergency Room – Hospital',
                                'Emergency Department', service_place))

lag_plot <- ggplot(lag_result, aes(x = Lag, y = estimate)) +
  geom_point(color = "#3c1053") + 
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), color = "#3c1053",width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~service_place, scales = "free_y", ncol = 2) +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in WFS PM"[2.5]))) +
  xlab("Lag") +
   # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element (tilt)
    axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.7),
    #axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90))

lag_plot
# save plot
# ggsave("./Figs/asthma_pos_lag_plot.tiff", lag_plot, 
#        units="in", width=8, height=6, dpi=300)
```
